### 2009-05-07 trunk/htdocs/sections.tex
Updates to references, tables
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@528 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  sections.tex
%
%  Content for Ludwig documentation.
%
%  $Id: sections.tex,v 1.5 2008-09-20 10:39:58 kevin Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2008 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The parameter $\kappa$

\inputkey{C}

The surface free energy parameter {C}. Currently unused.

\inputkey{H}

The surface free energy parameter {H}. Currently unused.

@@

The force exerted on a
single link is
\begin{equation}
\mathbf{F}_b(\mathbf{r} + {\scriptstyle\frac{1}{2}}\mathbf{c}_b\Delta t;
t + {\scriptstyle\frac{1}{2}}\Delta t) = \frac{\Delta x^3}{\Delta t}
\Big[ 2f_b^\ast(\mathbf{r}; t) - \frac{2w_{c_b}\rho_0 \mathbf{u}_b .
\mathbf{c}_b}{c_s^2} \Big] \mathbf{c}_b,
\end{equation}
with corresponding torque $\mathbf{T}_b = \mathbf{r}_b \times \mathbf{F}_b$.

@@

@@

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  sections.tex
%
%  Content for Ludwig documentation.
%
%  $Id: sections.tex,v 1.10 2009-05-07 15:29:05 kevin Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2008 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The parameter $\kappa$, which is positive.

\subsubsection{Brazovskii free energy}

This is similar to the symetric, but with one extra term which
requires description.
\begin{equation}
 F[\phi] = 
\int dr \left(
{\textstyle \frac{1}{2}}A\phi^2
+ {\textstyle \frac{1}{4}}B\phi^4
+ {\textstyle \frac{1}{2}}\kappa (\mathbf{\nabla}\phi)^2
+ {\textstyle \frac{1}{2}} C (\nabla^2 \phi)^2 \right).
\end{equation}

\subsubsection{Surfactant model free energy}

\inputkey{free\_energy surfactant}

This is for use with a two order parameter model the first of
which is the composition, as for the symmetric free energy,
while the second $\psi$ represents surfactant concentration.
The free energy density is made up of a number of terms:

\begin{equation}
{\textstyle \frac{1}{2}}A\phi^2
+ {\textstyle \frac{1}{4}}B\phi^4
+ {\textstyle \frac{1}{2}}\kappa (\mathbf{\nabla}\phi)^2
\end{equation}
is the standard symmetric term related to the composition as above;

\begin{equation}
D \left(\psi \ln\psi + (1 - \psi) \ln(1-\psi)\right)
\end{equation}
represents the energy of surfactant in the bluk phase with surfactant
concentration $0 < \psi < 1$ with a single parameter $D$;
\begin{equation}
-{\textstyle \frac{1}{2}} \epsilon \psi (\mathbf{\nabla} \phi)^2
-{\textstyle \frac{1}{2}} \beta \psi^2  (\mathbf{\nabla} \phi)^2
\end{equation}
where the term in $\epsilon$ represents the energy reduction by
adsorbing surfactant at the interface and the term in $\beta$
provides [TO BE ACCOUNTED FOR]; finally, there is an extra term
\begin{equation}
+{\textstyle \frac{1}{2}} W \psi \phi^2
\end{equation}
which is included to stabilise the interface \cite{theissengompper}.

The corresponding keys for the input file are:

\inputkey{D}

is the bulk surfactant contribution parameter

\inputkey{epsilon}

is the parameter $\epsilon$

\inputkey{W}

is the parameter $W$

\inputkey{beta}

is the value of the parameter $\beta$ (not implemented yet).

\inputkey{phi\_b}

the initial, uniform, background surfactant concentration $\psi_b$.

\subsection{Other Binary Fluid Parameters}

@@

The force exerted on a
single link is
\begin{equation}
\mathbf{F}_b(\mathbf{r} + {\scriptstyle\frac{1}{2}}\mathbf{c}_b\Delta t;
t + {\scriptstyle\frac{1}{2}}\Delta t) = \frac{\Delta x^3}{\Delta t}
\Big[ 2f_b^\ast(\mathbf{r}; t) - \frac{2w_{c_b}\rho_0 \mathbf{u}_b .
\mathbf{c}_b}{c_s^2} \Big] \mathbf{c}_b,
\label{eq:fb}
\end{equation}
with corresponding torque $\mathbf{T}_b = \mathbf{r}_b \times \mathbf{F}_b$.

@@

\section{Surfactants}

This section describes the approach taken to study surfactants. Here,
we always adopt the hydrid method, i.e., LB for the hydrodynmic
equations and finite difference for the associated Cahn-Hilliard
equations. Coupling between the two sectors is via the velocity
field and the external force on the fluid computed via the
divergence of the `chemical stress'.

In this model the surfactant appears as a concentration field
$\psi(\mathbf{r};t)$, alongside the compositional order parameter
$\phi(\mathbf{r};t)$ as appears in the binary fluid. There are
two corresponding Cahn-Hilliard equations: first,

\begin{equation}
\partial_t \phi + \partial_\alpha \phi u_\alpha = 
\partial_\alpha M_\phi \partial_\alpha \mu_\phi,
\end{equation}
and second
\begin{equation}
\partial_t \psi + \partial_\alpha \psi u_\alpha = 
\partial_\alpha M_\psi \partial_\alpha \mu_\psi.
\end{equation}

\subsection{Free Energy}

A number of different free energies have been used to study
surfactants [cite Yeomans]. Here, the free energy is based on
that used by van der Graff and van der Sman and others [cite].
There are a number of different contributions to the free
energy density:
\begin{equation}
f = f_\phi + f_\psi +f_1 + f_{ex}.
\end{equation}
The first is exactly that used for the binary fluid, i.e.,
\begin{equation}
f_\phi (\phi, \partial_\alpha\phi) =
{\textstyle \frac{1}{2}} A \phi^2 + {\textstyle \frac{1}{4}} B \phi^4
+ {\textstyle \frac{1}{2}} \kappa (\partial_\alpha \phi)^2.
\end{equation}
The surface tension and the interfacial width are determined from the
choice of parameters $A,B,\kappa$ as before.
The second term in the free energy density
represents the entropic
energy of mixing of the surfactant with the bulk phases
\begin{equation}
f_\psi (\psi) = kT \left[ \psi \ln\psi + (1 - \psi)\ln(1-\psi) \right]
\end{equation}
where the parameter $kT$ sets the energy scale for the whole system.
The surfactant order parameter, $\psi$, is unity for a saturated
interface and zero for a plain interface.

The surfactant lowers the energy of the interface where it is adsorbed
there, represented by the term
\begin{equation}
f_1(\psi, \partial_\alpha \phi) 
= -{\textstyle \frac{1}{2}} \epsilon \psi (\partial_\alpha \phi)^2
  -{\textstyle \frac{1}{2}} \beta  \psi^2 (\partial_\alpha \phi)^2
\end{equation}
where $\epsilon$ and $\beta$ are parameters. Note that only the
first term appears in \cite{vandergraaf}, while the second term is
based on that appearing in, e.g., \cite{diamant}. If $\beta = 0$,
the surfactant profile at the interface is symmetric (so-called
Langmuir adsoption) whereas the term in $\beta$ induces an
asymmetry (Frumpkin adsorption).
Finally,  $f_{ex}$ is [van der Sman claims]
an enthalpic contribution introduced 
to stabilise the interface \cite{theissengompper}
\begin{equation}
f_{ex} (\psi, \partial_\alpha \phi) = {\textstyle\frac{1}{2}} W \psi \phi^2,
\end{equation}
with $W$ a parameter.

\subsection{Chemical potentials}

The respective chemical potentials are obtained from the functional
derivatives of the free energy $\mu_\phi = \delta F / \delta \phi$ and
$\mu_\psi = \delta F / \delta \psi$. We obtain:
\begin{equation}
\mu_\phi =
A\phi + B\phi^3 -\kappa \partial_\alpha^2 \phi
+ W\psi\phi + \epsilon\psi\partial_\alpha^2 \phi
+ \epsilon \partial_\alpha \phi \partial_\alpha \psi
+ 2\beta \psi\partial_\alpha\phi \partial_\alpha \psi
+ \beta \psi^2 \partial_\alpha^2 \phi,
\end{equation}
and
\begin{equation}
\mu_\psi = kT \left[ \ln\psi - \ln(1-\psi) \right]
+ {\textstyle \frac{1}{2}}W\phi^2
- {\textstyle \frac{1}{2}}\epsilon (\partial_\alpha \phi)^2
- \beta\psi (\partial_\alpha \phi)^2.
\end{equation}
As before, the pressure tensor is $P_{\alpha\beta} = p_0\delta_{\alpha\beta}
+ \tilde{P}_{\alpha\beta}$ with the isotropic part being determined as (e.g.,
\cite{theissengompper})
\begin{equation}
p_0 = \phi \mu_\phi + \psi \mu_\psi - f(\phi, \psi, \partial_\alpha \phi).
\end{equation}
There is no closed form for the tensor part, which must be chosen to
comply with the constraint that in mechanical equilibrium
\begin{equation}
\partial_\alpha P_{\alpha\beta} = (\phi\partial_\alpha\mu_\phi +
\psi\partial_\alpha\mu_\psi)\delta_{\alpha\beta}.
\end{equation}
In this way we obtain for the isotropic contribution
\begin{eqnarray}
p_0 = {\textstyle \frac{1}{2}}A\phi^2 + {\textstyle \frac{3}{4}}B\phi^4 
- {\textstyle\frac{1}{2}}\kappa (\partial_\alpha\phi)^2 
- \kappa \phi \partial_\alpha^2 \phi
- kT \ln(1-\psi) + W\psi\phi^2
\nonumber\\
+ \epsilon \phi \partial_\alpha \phi \partial_\alpha \psi
+ \epsilon\phi\psi \partial_\alpha^2 \phi
+ 2 \beta\phi\psi \partial_\alpha \phi \partial_\alpha\psi
+ \beta \phi \psi^2 \partial_\alpha^2 \phi
- {\textstyle\frac{1}{2}} \beta \psi^2 (\partial_\alpha \phi)^2
\end{eqnarray}
and for the tensor part we can have
\begin{equation}
\tilde{P}_{\alpha\beta} =
(\kappa - \epsilon \psi - \beta\psi^2) 
\partial_\alpha \phi \partial_\beta \phi.
\end{equation}

@@

\bibitem{chang}
C.-H. Chang and E.I. Franses,
Adsorption dynamics of surfactants at the air/water interface:
a critical review of mathematical models, data, and mechanisms,
\textit{Colloids and Surfaces A}, \textbf{100} 1, 1995.

@@

\bibitem{diamant}
H. Diamant and D. Andelman,
Kinetics of surfactant adsorption at fluid/fluid
interfaces: non-ionic surfactants,
\textit{Europhys. Lett.} \textbf{34}, 575 (1996).

\bibitem{diamant96}
H. Diamant and D. Andelman,
Kinetics of surfactant adsorption at fluid-fluid interfaces,
\textit{J. Phys. Chem.}, \textbf{100} 13732, 1996.

\bibitem{eastoe}
J. Eastoe and J.S. Dalton,
Dynamic surface tension and adsorption mechanims of surfactants
at the air-water interface,
\textit{Advances in Colloid and Interface Science}, \textbf{85}
13, 2000.

@@

\bibitem{vandergraaf}
R.G.M. van der Sman and S. van der Graaf,
Diffuse interface model of surfactant adsorption onto flat and
droplet interfaces,
\textit{Rheol. Acta} \textbf{46} 3 (2006).

\bibitem{theissengompper}
O. Theissen and G. Gompper,
Lattice Boltzmann study of spontaneous emulsification,
\textit{Eur. Phys. J. B}, \textbf{11} 91 (1999).

\bibitem{wardtordai}
A.F.H. Ward and L. Tordai,
\textit{J. Chem. Phys.} \textbf{14} 453, 1946.

### 2009-05-07 trunk/htdocs/surfactant.tex
Updates to references, tables
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@528 40876441-3496-0410-a613-a2fca35b2ae2

To this we add a separate order parameter to represent the
surfactant $\psi$ \cite{smangraaf}. The free energy density
is made up of two parts following DA96:
\begin{equation}
f_{\psi} = kT[\psi\ln\psi  + (1 - \psi) \ln (1 - \psi)]
\end{equation}
represents the entropy of mixing, valid in both the bulk and at
the interface. The interfacial part of the free energy density is
\begin{equation}
f_{\psi,i} = -{\textstyle\frac{1}{2}}\epsilon\psi (\partial_\alpha \phi)^2
- {\textstyle\frac{1}{2}} \beta \psi^2 (\partial_\alpha \phi)^2.
\end{equation}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
Name & $\eta$ & $-A,B$ & $\kappa$ & $kT$ & $\epsilon$ & $\beta$ & $W$
     & $M$ & $M_\psi$\\
\hline
R008a & 1/6 & 0.0625 & 0.04 & 1.6965$\times 10^{-3}$ & 0.01 & 0.0000 & 0.0 
      & 0.15 & 1.0 \\
R008d &  &  &  & & & 0.0025 &  &  &  \\
R008f &  &  &  & & & 0.0050 &  &  &  \\
\hline
R006a & 1/6 & 0.0625 & 0.04 & 8.48231$\times 10^{-4}$ & 0.01 & 0.0000 & 0.0 
      & 0.15 & 1.0 \\
R006d & &  &  &  & & 0.0025 &  &  &  \\
R006f & &  &  &  & & 0.0050 &  &  &  \\
\hline
\end{tabular}
\caption{Parameters}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & $\bar{\psi}$ & $\psi_b$ & $\psi_{0\mathrm{eq}}$
     & $\sigma / \sigma_0$  & Comment \\
\hline
R008a &  $2.0\times 10^{-1}$ & $1.859\times 10^{-1}$ & $5.143\times10^{-1}$
      & 0.76 & ok\\
R008a &  $1.0\times 10^{-1}$ & $9.093\times 10^{-2}$ & $3.033\times10^{-1}$
      & 0.80 & ok\\
R008a &  $5.0\times 10^{-2}$ & $4.490\times 10^{-2}$ & $1.643\times10^{-1}$
      & 0.82 & ok\\
R008a &  $2.5\times 10^{-2}$ & $2.231\times 10^{-2}$ & $8.540\times10^{-2}$
      & 0.84 & ok\\
R008a &  $1.0\times 10^{-2}$ & $8.888\times 10^{-3}$ & $3.494\times10^{-2}$
      & 0.86 & ok\\
R008a &  $1.0\times 10^{-3}$ & $8.867\times 10^{-4}$ & $3.540\times10^{-3}$
      & 0.87 & ok\\
\hline
R008d &  $2.0\times 10^{-1}$ &  &  &  & unstable \\
R008d &  $1.0\times 10^{-1}$ &  &  &  & unstable \\
R008d &  $5.0\times 10^{-2}$ &  &  &  & unstable \\
R008d &  $2.5\times 10^{-2}$ &  &  &  & no equilibrium \\
R008d &  $1.0\times 10^{-2}$ & $8.455\times 10^{-3}$ & $4.535\times10^{-2}$
      & 0.85 & ok \\
R008d &  $1.0\times 10^{-3}$ & $8.835\times 10^{-4}$ & $3.617\times10^{-3}$
      & 0.87 & ok \\
\hline
R006a &  $2.0\times 10^{-1}$ & $1.713\times 10^{-1}$ & $8.510\times10^{-1}$
      & 0.71 & ok\\
R006a &  $1.0\times 10^{-1}$ & $7.556\times 10^{-2}$ & $6.657\times10^{-1}$
      & 0.74 & ok\\
R006a &  $5.0\times 10^{-2}$ & $3.406\times 10^{-2}$ & $4.211\times10^{-1}$
      & 0.78 & ok\\
R006a &  $2.5\times 10^{-2}$ & $1.616\times 10^{-2}$ & $2.310\times10^{-1}$
      & 0.81 & ok\\
R006a &  $1.0\times 10^{-2}$ & $6.286\times 10^{-3}$ & $9.653\times10^{-2}$
      & 0.84 & ok\\
R006a &  $1.0\times 10^{-3}$ & $6.192\times 10^{-4}$ & $9.868\times10^{-3}$
      & 0.87 & ok\\
\hline
R006d &  $2.0\times 10^{-1}$ & $1.664\times 10^{-1}$ & $9.791\times10^{-1}$
      & 0.64 & ok\\
R006d &  $1.0\times 10^{-1}$ &  & &  & unstable\\
R006d &  $5.0\times 10^{-2}$ &  & &  & unstable\\
R006d &  $2.5\times 10^{-2}$ &  & &  & unstable\\
R006d &  $1.0\times 10^{-2}$ & $2.9\times 10^{-4}$ & $4.75\times10^{-1}$
      & 0.80 & unsymmetric\\
R006d &  $1.0\times 10^{-3}$ & $5.822\times 10^{-4}$ & $1.077\times10^{-2}$
      & 0.87 & ok \\
\hline
\end{tabular}
\label{table:xi113}
\caption{Equilibrium results for $\xi_0 = 1.13$, $\epsilon = \kappa/4$.}
\end{center}
\end{table}

@@

>>>>

To this we add a separate order parameter to represent the
surfactant $\psi$ \cite{vandergraaf}. The free energy density
is made up of two parts following DA96:
\begin{equation}
f_{\psi} = kT[\psi\ln\psi  + (1 - \psi) \ln (1 - \psi)]
\end{equation}
represents the entropy of mixing, valid in both the bulk and at
the interface. The interfacial part of the free energy density is
\begin{equation}
f_{\psi,i} = -{\textstyle\frac{1}{2}}\epsilon\psi (\partial_\alpha \phi)^2
- {\textstyle\frac{1}{2}} \beta \psi^2 (\partial_\alpha \phi)^2.
\end{equation}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
Name & $\eta$ & $-A,B$ & $\kappa$ & $kT$ & $\epsilon$ & $\beta$ & $W$
     & $M$ & $M_\psi$\\
\hline
R008a & 1/6 & 0.0625 & 0.04 & 1.6965$\times 10^{-3}$ & 0.01 & 0.0000 & 0.0 
      & 0.15 & 1.0 \\
R008d &  &  &  & & & 0.0025 &  &  &  \\
\hline
R006a & 1/6 & 0.0625 & 0.04 & 8.48231$\times 10^{-4}$ & 0.01 & 0.0000 & 0.0 
      & 0.15 & 1.0 \\
R006d & &  &  &  & & 0.0025 &  &  &  \\
\hline
R010a & 0.025 & 0.00625 & 0.004 & 1.6965$\times 10^{-4}$ & 0.001
      & 0.0000 & 0.0 & 2.0 & 2.0 \\
R010d & &  &  &  & & 0.0005 &  &  &  \\
\hline
R012a & 0.025 & 0.00625 & 0.004 & 8.48231$\times 10^{-5}$ & 0.001
      & 0.0000 & 0.0 & 2.0 & 2.0 \\
R012d & &  &  &  & & 0.0005 &  &  &  \\
\hline
\end{tabular}
\caption{Parameters for $\xi_0 = 1.13$ and $\epsilon = \kappa/4$.}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & $\bar{\psi}$ & $\psi_b$ & $\psi_{0\mathrm{eq}}$
     & $\sigma / \sigma_0$  & Comment \\
\hline
R008a &  $2.0\times 10^{-1}$ & $1.859\times 10^{-1}$ & $5.143\times10^{-1}$
      & 0.76 & ok\\
R008a &  $1.0\times 10^{-1}$ & $9.093\times 10^{-2}$ & $3.033\times10^{-1}$
      & 0.80 & ok\\
R008a &  $5.0\times 10^{-2}$ & $4.490\times 10^{-2}$ & $1.643\times10^{-1}$
      & 0.82 & ok\\
R008a &  $2.5\times 10^{-2}$ & $2.231\times 10^{-2}$ & $8.540\times10^{-2}$
      & 0.84 & ok\\
R008a &  $1.0\times 10^{-2}$ & $8.888\times 10^{-3}$ & $3.494\times10^{-2}$
      & 0.86 & ok\\
R008a &  $1.0\times 10^{-3}$ & $8.867\times 10^{-4}$ & $3.540\times10^{-3}$
      & 0.87 & ok\\
\hline
R008d &  $2.0\times 10^{-1}$ &  &  &  & unstable \\
R008d &  $1.0\times 10^{-1}$ &  &  &  & unstable \\
R008d &  $5.0\times 10^{-2}$ &  &  &  & unstable \\
R008d &  $2.5\times 10^{-2}$ &  &  &  & no equilibrium \\
R008d &  $1.0\times 10^{-2}$ & $8.455\times 10^{-3}$ & $4.535\times10^{-2}$
      & 0.85 & ok \\
R008d &  $1.0\times 10^{-3}$ & $8.835\times 10^{-4}$ & $3.617\times10^{-3}$
      & 0.87 & ok \\
\hline
R006a &  $2.0\times 10^{-1}$ & $1.713\times 10^{-1}$ & $8.510\times10^{-1}$
      & 0.71 & ok\\
R006a &  $1.0\times 10^{-1}$ & $7.556\times 10^{-2}$ & $6.657\times10^{-1}$
      & 0.74 & ok\\
R006a &  $5.0\times 10^{-2}$ & $3.406\times 10^{-2}$ & $4.211\times10^{-1}$
      & 0.78 & ok\\
R006a &  $2.5\times 10^{-2}$ & $1.616\times 10^{-2}$ & $2.310\times10^{-1}$
      & 0.81 & ok\\
R006a &  $1.0\times 10^{-2}$ & $6.286\times 10^{-3}$ & $9.653\times10^{-2}$
      & 0.84 & ok\\
R006a &  $1.0\times 10^{-3}$ & $6.192\times 10^{-4}$ & $9.868\times10^{-3}$
      & 0.87 & ok\\
\hline
R006d &  $2.0\times 10^{-1}$ & $1.664\times 10^{-1}$ & $9.791\times10^{-1}$
      & 0.64 & ok\\
R006d &  $1.0\times 10^{-1}$ &  & &  & unstable\\
R006d &  $5.0\times 10^{-2}$ &  & &  & unstable\\
R006d &  $2.5\times 10^{-2}$ &  & &  & unstable\\
R006d &  $1.0\times 10^{-2}$ & $2.9\times 10^{-4}$ & $4.75\times10^{-1}$
      & 0.80 & unsymmetric\\
R006d &  $1.0\times 10^{-3}$ & $5.822\times 10^{-4}$ & $1.077\times10^{-2}$
      & 0.87 & ok \\
\hline
R010a & $2.0\times 10^{-1}$ & $1.859\times 10^{-1}$ & $5.143\times10^{-1}$
      & 0.76 & ok \\
R010a & $1.0\times 10^{-1}$ & $9.093\times 10^{-2}$ & $3.033\times10^{-1}$
      & 0.80 &  ok\\
R010a & $5.0\times 10^{-2}$ & $4.490\times 10^{-2}$ & $1.643\times10^{-1}$
      & 0.82 & ok \\
R010a & $2.5\times 10^{-2}$ & $2.231\times 10^{-2}$ & $8.540\times10^{-2}$
      & 0.84 & ok \\
R010a & $1.0\times 10^{-2}$ & $8.888\times 10^{-3}$ & $3.494\times10^{-2}$
      & 0.86 & ok \\
R010a & $1.0\times 10^{-3}$ & $8.867\times 10^{-4}$ & $3.540\times10^{-3}$
      & 0.87 & ok \\
\hline
R010d & $2.0\times 10^{-1}$ & $1.715\times 10^{-1}$ & $8.685\times10^{-1}$
      & 0.62 & ok \\
R010d & $1.0\times 10^{-1}$ & $8.327\times 10^{-2}$ & $4.893\times10^{-1}$
      & 0.73 & ok \\
R010d & $5.0\times 10^{-2}$ & $4.317\times 10^{-2}$ & $2.061\times10^{-1}$
      & 0.81 & ok \\
R010d & $2.5\times 10^{-2}$ & $2.190\times 10^{-2}$ & $9.524\times10^{-2}$
      & 0.84 & ok \\
R010d & $1.0\times 10^{-2}$ & $8.824\times 10^{-3}$ & $3.646\times10^{-2}$
      & 0.86 & ok \\
R010d & $1.0\times 10^{-3}$ & $8.861\times 10^{-4}$ & $3.555\times10^{-3}$
      & 0.87 & ok \\
\hline
R012a & $2.0\times 10^{-1}$ & $1.72\times 10^{-1}$ & $8.51\times10^{-1}$
      & 0.71 &  not quite at eqbm.\\
R012a & $1.0\times 10^{-1}$ & $7.5\times 10^{-2}$ & $6.63\times10^{-1}$
      & 0.74 &  not quite at eqbm.\\
R012a & $5.0\times 10^{-2}$ & $3.4\times 10^{-2}$ & $4.15\times10^{-1}$
      & 0.78 &  not quite\\
R012a & $2.5\times 10^{-2}$ & $1.6\times 10^{-2}$ & $2.26\times10^{-1}$
      & 0.82 &  not quite\\
R012a & $1.0\times 10^{-2}$ & $6.4\times 10^{-3}$ & $9.4\times10^{-2}$
      & 0.85 & not quite \\
R012a & $1.0\times 10^{-3}$ & $6.3\times 10^{-4}$ & $9.6\times10^{-3}$
      & 0.87 &  not quite\\
\hline
\end{tabular}
\label{table:xi113}
\caption{Equilibrium results for $\xi_0 = 1.13$, $\epsilon = \kappa/4$
at 2 million time steps.
Sets R006 and R008 have viscosity $\eta = 1/6$, while R010 and R012
have $\eta = 0.025$, showing very little sensitivity to viscosity.}
\end{center}
\end{table}

@@

\subsubsection{Parameters with $\xi_0 = 3.39$, $\epsilon = kappa/4$}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline
Name & $\eta$ & $-A,B$ & $\kappa$ & $kT$ & $\epsilon$ & $\beta$ & $W$
     & $M$ & $M_\psi$\\
\hline
R014a & 1/6 & 0.020833 & 0.12 & 5.6587$\times 10^{-4}$ & 0.03 & 0.0000 & 0.0 
      & 0.15 & 2.0 \\
R014d &  &  &  & & & 0.0075 &  &  &  \\
\hline
R016a & 1/6 & 0.020833 & 0.12 & $2.82743\times 10^{-4}$ & 0.03 & 0.0000 & 0.0 
      & 0.15 & 2.0 \\
R016d & &  &  &  & & 0.0075 &  &  &  \\
\hline
R018a & 0.025 & 0.0020833 & 0.012 & 5.6587$\times 10^{-5}$ & 0.003
      & 0.0000 & 0.0 & 2.0 & 2.0 \\
R018d & &  &  &  & & 0.00075 &  &  &  \\
\hline
R020a & 0.025 & 0.0020833 & 0.012 & 2.82743$\times 10^{-5}$ & 0.003
      & 0.0000 & 0.0 & 2.0 & 2.0 \\
R020d & &  &  &  & & 0.0075 &  &  &  \\
\hline
\end{tabular}
\caption{Parameters for $\xi_0 = 3.39$ and $\epsilon = \kappa/4$.}
\end{center}
\end{table}
